\documentclass{resume} % Use the custom resume.cls style
\usepackage[none]{hyphenat}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,      
  urlcolor=blue,
  pdftitle={Vu-Hong-Hai Phan's Resume},
  pdfpagemode=FullScreen,
  }

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Vu-Hong-Hai (Hai) Phan}
\email{honghaipvu@gmail.com}
\phone{(514)-XXX-XXXX}
\address{Montreal, QC, Canada \\ (open to relocation)}
\linkedin{linkedin.com/in/vhhphan}
\github{github.com/HongHaiPV}


\begin{document}
%%%
%%%
%%%
\begin{rSection}{EDUCATION}
\begin{rSchool}{Concordia University, Montreal}
  {\textbf{Winter 2020} - \textbf{Fall 2022}}
  {Master of Computer Science ({thesis})}
  {GPA: 4.0/4.3}
  {Awards: Mitacs research fellowship (\$40k), Concordia FRS bursaries (\$15k).}
\end{rSchool}
%
\begin{rSchool}{Hanoi University of Science and Technology (HUST)}
  {\textbf{Fall 2014} - \textbf{Fall 2019}}
  {Bachelor of Computer Science ({5-years program})}
  {GPA: 3.51/4.0}
  {Awards: In-course scholarships, 3rd-prize competitive programming ({university-level}).}
\end{rSchool}
\end{rSection}
%%%
%%%
%%%
\begin{rSection}{EXPERIENCES}
\begin{rWork}{Research Consultant (Mitacs)}{EXFO Inc, Montreal}{April 2020 - April 2022}
  \item Engineered scalable and interpretable machine learning algorithm for automated root cause analysis using Python+Spark, increasing the diagnosis speed by 20x.
  \item Surveyed and performed experiments on causal modelling, resulting in a well-received 2 years research plan and providing demonstrations every month.
  \item Collaborated with team of domain experts, published 10+ internal documents and codes; one patent and one conference paper (both first-authored).
\end{rWork}
%
\begin{rWork}{Data Scientist}{Viettel, Hanoi}{Jun. 2019 - Nov. 2019}
  \item Architected recommender systems using Python, Hive, Spark and Redis, serving 1M+ customers daily, in soft real-time, with 5x pickup rates uplift, averaging \$100,000 USD revenue/month.
  \item Developed proprietary framework for large-scale RCT, supporting A/B testing and multi-armed bandit, with automated reporting features.
  \item Overhauled music recommender system using topic modeling, achieving 10x pickup rate increase.
\end{rWork}
%
\begin{rWork}{Research Assistant}{HUST, Hanoi}{Mar. 2017 - Jun. 2019}
  \item Engineered DL translation model in Tensorflow, bested Google \& Bing Translate in BLEU metric.
  \item Collected, pre-processed corpus data using Python and web crawlers, resulting in nearly 1M pair of sentences.
  \item Coordinated research team of six people, published multiple papers and seminars, of which two are first authored.
\end{rWork}
%
\begin{rWork}{Software Engineer (part-time)}{Viettel, Hanoi}{May 2017 - Jun. 2018}
  \item Architected and maintained set of RESTful endpoints for chatbot, using Java, Python Flask, C++ and Apache Solar, achieving classification accuracy of 99\%.
  \item Developed automatic data filtering process using Python + MySQL to move data to labelling platform, reduced low-quality data by 50\% as well as reduced idle time and improved labeling quality.
\end{rWork}
\end{rSection}
%%%
%%%
%%%
\begin{rSection}{Projects}
\textbf{Arithmetic Encoder (2023)-\href{https://github.com/HongHaiPV/ArithmeticEncoder}{Github}.} A Python library for encoding and decoding text data using statistical estimators.
\end{rSection}
%%%
%%%
%%%
\begin{rSection}{SKILLS}
\textbf{Languages:} Python, Java, SQL, C/C++, \LaTeX, Bash, Matlab/Octave, HTML/CSS, Scala\\
\textbf{Frameworks:} Pandas, PyTorch, Tensorflow, Numpy, Scikit-learn, Plotly, Flask, PyTest, XGBoost, SciPy, Apache Hadoop, Apache Spark, Git, Docker, Gitlab CI/CD, Jenkins, Pentaho DI , MySQL, ORACLE, MSSQL(exposure), Redis, MongoDB, Tableau (exposure), GCP (exposure), AWS (exposure)\\
\textbf{Natural Languages:} English (fluent), French (elementary), Vietnamese (native)\\
\end{rSection}
%%%
%%%
%%%
\end{document}
